---
title: "Sepsis: Report"
author: "Subin Jang"
format: 
 html:
    theme: simplex
    embed-resources: true
execute:
  warning: false
  message: false
  echo: true
editor: visual
---

### **ICU status report**

```{r}
#| echo: false
#| message: false

library(googledrive)
library(tidyverse)
library(lubridate)
source("sepsis_monitor_functions.R")

## Calling drive_deauth() prevents R from trying to authenticate via a browser
## This is needed to make the GitHub Action work
drive_deauth()
file_link <- "https://drive.google.com/file/d/1H28fF1ZBD32QWm2ZBglORVwwzuZSLMu9/view"

## All data up until now
new_data <- updateData(file_link)

## Include only most recent data
most_recent_data <- new_data %>%
  group_by(PatientID) %>%
  filter(obsTime == max(obsTime))
```

### *This report was created on **`r Sys.time()`***

#### A table listing the patients who currently have sepsis (if any), along with their most recent heart rate, temperature, and respiratory rate

```{r}
#| echo: false
#| message: false

library(dplyr)
library(knitr)
library(kableExtra)
library(tibble)
library(gt)

most_recent_data %>% 
  filter(SepsisLabel == 1) %>%
  ungroup() %>%
  gt()
```

#### Plots for all patients who have sepsis (if any) that show the complete history of their heart rate, temperature, and respiratory rate during their time in the ICU.

```{r}
#| echo: false
#| message: false
#| warning: false

library(ggplot2)

sepsisPatient <- most_recent_data %>%
  filter(SepsisLabel ==1)

new_data %>%
  filter(PatientID %in% sepsisPatient$PatientID) %>%
  pivot_longer(3:5, names_to = "Measures" , values_to = "Values") %>%
  ggplot(aes(x= obsTime, y= Values, color= PatientID)) +
  scale_x_datetime(date_labels = "%Y-%m-%d %H:%M:%S")+
  geom_point() +
  geom_line() +
  facet_wrap(~ Measures, ncol=3)+
  labs(Title = "Changes in clinical measures over time", x = "obsTime", y = "Value")+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90))
  
# new_data %>%
#   group_by(PatientID) %>%
#   filter(obsTime == max(obsTime)) %>% 
#   filter(SepsisLabel == 1) %>% 
#   ungroup() %>% 
#   {filter(new_data, PatientID %in% .$PatientID)} %>%
#   pivot_longer(3:5, names_to = "Measures" , values_to = "Values") %>%
#   ggplot(aes(x= ICULOS, y= Values, color= PatientID)) +
#   geom_point() +
#   geom_line() +
#   facet_wrap(~ Measures, ncol=3) +
#   labs(Title = "Changes in clinical measures over time", x = "Time in ICU", y = "Value")+
#   theme(legend.position = "none")
```

#### A table showing the *change* in heart rate, temperature, and respiratory rate between the last two measurements for all patients

```{r}
#| echo: false

new_data %>%
  group_by(PatientID) %>%
  mutate(changeHR = HR - lag(HR, n=1, default= NA),
         changeTemp = Temp - lag(Temp, n=1, default= NA),
         changeResp = Resp - lag(Resp, n=1, default= NA)) %>%
  filter(obsTime == max(obsTime)) %>%
  ungroup() %>%
  gt() %>%
    tab_style(
    style = cell_fill(color = "pink"),
    locations = cells_body(
      columns = changeHR,
      rows = changeHR < 0)) %>%
        
    tab_style(
    style = cell_fill(color = "pink"),
    locations = cells_body(
      columns = changeTemp,
      rows = changeTemp < 0)) %>%
  
      tab_style(
    style = cell_fill(color = "pink"),
    locations = cells_body(
      columns = changeResp,
      rows = changeResp < 0)) %>%
  
  tab_style(
    style = cell_fill(color = "green"),
    locations = cells_body(
      columns = changeHR,
      rows = changeHR > 0)) %>%
  
  tab_style(
    style = cell_fill(color = "green"),
    locations = cells_body(
      columns = changeTemp,
      rows = changeTemp > 0)) %>%
  
  tab_style(
    style = cell_fill(color = "green"),
    locations = cells_body(
      columns = changeResp,
      rows = changeResp > 0)) %>%
  
    tab_style(
    style = cell_fill(color = "yellow"),
    locations = cells_body(
      columns = changeHR,
      rows = changeHR == 0)) %>%
  
  tab_style(
    style = cell_fill(color = "yellow"),
    locations = cells_body(
      columns = changeTemp,
      rows = changeTemp == 0)) %>%
  
  tab_style(
    style = cell_fill(color = "yellow"),
    locations = cells_body(
      columns = changeResp,
      rows = changeResp ==0 )) %>%
  
      tab_style(
    style = cell_fill(color = "grey"),
    locations = cells_body(
      columns = changeHR,
      rows = is.na(changeHR))) %>%
  
  tab_style(
    style = cell_fill(color = "grey"),
    locations = cells_body(
      columns = changeTemp,
      rows = is.na(changeTemp))) %>%
  
  tab_style(
    style = cell_fill(color = "grey"),
    locations = cells_body(
      columns = changeResp,
      rows = is.na(changeResp)))

```
